---
title: "HW1-33B"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Call Expressions

The standard normal curve is centered at 0 and has a spread, AKA standard deviation, of 1. This curve is drawn in the figure below along with a normal curve that has a center of 2 and a spread of 1.5 (dashed curve).

```{r}
curve(dnorm, from = -3, to = 6, ylab = "Density")
curve(dnorm(x, mean = 2, sd = 1.5), add = TRUE, lty = 2)
```


The family of normal curves all have the same shape and each is uniquely specified by its center (mean) and spread (standard deviation)  


1. Read the documentation for `rnorm()` to figure out how to call `rnorm()` to generate 5 random values from a normal distribution with mean 17 and standard deviation 3.
```{r}
res = rnorm(5, mean=17, sd=3)
```

Debug: Result is `r res`.

2. Create a vector called `normSamps` containing 1000 random values from a normal distribution with mean 1 and standard deviation 2.
```{r}
set.seed(66)
normSamps = rnorm(1000, mean=1, sd=2)
```

3. The 10% trimmed mean is obtained by taking the mean of the middle 80% of the values (removing the lowest 10% and the highest 10% of the values). Find the 10% trimmed mean of normSamps and assign this value to `mean10`. 
Hint: Look at the help file for the mean() function.
```{r}
mean10 = mean(normSamps, trim=0.1)
```

Debug: Result is `r mean10`.

4. Use `sum()` to calculate the fraction of values in 
`normSamps` that are less than 3. 
Write your solution so that it coerces a logical vector to numeric without using the function as.numeric().
Write your code generically so that it doesn't depend on
`normSamps` being a vector of 1000 elements.
Assign the fraction to the variable `frac3`
Hint: consider using the `length()` function.
```{r}
# It maybe slow and expensive to create a useless vector by filter.
#   (REALLY REALLY slow in traditional programming language, but maybe there's strange optimization in R ?)
isLessThan3 = Vectorize(function(ele) {
    return(ele < 3) # Strange R syntax...
})
frac3 = length(normSamps[isLessThan3(normSamps)]) / length(normSamps)
```

Debug: Result is `r frac3`.

5. A percentile is the value at which a given percentage of samples fall at or below it and is sometimes synonomously called a quantile, e.g., the 90th percentile is the value at which 90% of data values fall at or below it. Calculate the 90th percentile of `normSamps` and assign this value to `per90`. 
Hint: The `quantile()` function is helpful for this question.
```{r}
# Replace the 1 on the right hand side of the equation with your code
per90 = quantile(normSamps, probs=c(0.9))
```

Debug: Result is `r per90`.

6. Calculate the greatest absolute distance from 1 for the values in `normSamps`. Assign this value to a variable called `maxDev`, short for "maximum deviation" from the mean. Hint: The functions abs() and max() are helpful for this question.
```{r}
# Replace the 1 on the right hand side of the equation with your code
maxDev = 1
```

## Working with Vectors

Run the following code chunk to load the vectors for our 14-member family:
```{r}
load(url("http://www.stat.berkeley.edu/users/nolan/data/afamily.rda"))
```

7. Calculate `bmi` from `fheight` and `fweight` by dividing weight in pounds by height in inches squared and multiplying by a conversion factor of 703. Assign this to `bmi_alt`
```{r}
# Replace the 1 on the right hand side of the equation with your code
bmi_alt = 1
```

8. Check that `fbmi` and `bmi_alt` match using the functions `==` and `all()`
```{r}

```

9. Suppose that as long as the entries in `bmi_alt` and `fbmi` are within 0.1 of each other, then we consider these two to be equivalent. 
Calculate the differences and assign it to `bmi_diff`.  
Check whether all of the differences are within 0.1 of each other. 
Produce a logical vector of length 1 called `bmi_same` 
that is TRUE if the entries in `bmi_alt` and `fbmi` are 
within 0.1 of each other.
```{r}
bmi_diff = 1

bmi_same = 1
```

10. Create a vector of last names for the family members, called `flast`. The values should be `Smith` for each entry.
Hint: use `rep()` and `length()` to do this.
```{r}
flast = 1
```


